---
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
header-includes:
output: pdf_document
---

```{r setup0, echo=FALSE,purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Question 0**

```{r}
# This is a code chunk.
# Furthermore, the '#' is used for comments and turns the text green.
# Comments are not executed when running the contents of a code chunk.
# Comments are important - read them!

# Assign the value 2 to X:
X <- 2
# Display X
X
# Define Y as a vector containing the values 1,2,3,4
Y <- c(1,2,3,4)
# Display Y
Y
# Values of a vector need not be numbers.
# For example, S is defined as the sample space from the "Family Planning" in the lecture notes:
S <- c("MMM","FFF","MFM","FMM","MMF","MFF","FMF","FFM")
# Display S
S
```

**Question 1 part (a)**

```{r}
# Replace "NULL" with the proper code.
A <- c("LLL","RRR","SSS")
B <- c("RLS", "RSL", "LRS", "LSR", "SRL", "SLR")
C <- c("RRL", "RRS", "RLR", "RSR", "LRR", "SRR")
D <- c(C, "LLR", "LLS", "LRL", "LSL", "RLL", "SLL", "SSR", "SSL", "SRS", "SLS", "RSS", "LSS")

```

**Question 1 part (b)**

```{r}
# Replace "NULL" with the proper code.
E <- union(C,D)
G <- intersect(C,D)

```

**Question 2**

```{r}
# Type "?c" below and run the code chunk.
?c
```

Read the description. What could the letter 'c' stand for in this function? **Type your answer below:** conctenate

**Question 3 part (a)**

```{r}
# This code is a function that simulates n rolls of two fair multi-sided dice.
# Each roll, the dice results are added together and stored in a vector called results.
dice_roll <- function(sides=6,rolls=1) {
  # initialize the results vector (empty to begin)
  results <- c()
  # initiate a for loop to run 'rolls' times
  for (i in 1:rolls) {
    # simulate the rolling of two die (randomly select two values from {1,2,3,..,'sides'})
    roll <- sample(1:sides,size=2,replace=TRUE)
    # sum the results of the roll (result will be a number between 2 and 2*sides) and put the total in the results vector
    results <- c(results,sum(roll))
  }
  # print the results
  return(results)
}
# Execute this code chunk before proceeding.
```

**Question 3 part (b)**

```{r}
# Test the dice_roll function below
dice_roll(sides = 8, rolls = 1) 
dice_roll(sides = 9, rolls = 10)

```

**Question 3 part (c)**

```{r}
# Replace "NULL" with the proper code.
rolls_500 <- dice_roll(sides = 9, rolls = 500)
table(rolls_500)
barplot(table(rolls_500))
```

### Submission Instructions

1.  Save this file. (Quick key combo for that is "control" (or "command" on a Mac) and "s")
2.  Run the following code chunk to produce a pdf.
3.  Both of these files are likely in the "Downloads" folder (unless you moved them). Check the contents of each file and upload both the Rmd and pdf files to Gradescope.

```{r, echo=FALSE ,eval=FALSE,purl=FALSE}
rstudioapi::documentSave(rstudioapi::getSourceEditorContext()$id)
rmarkdown::render(rstudioapi::getSourceEditorContext()$path,output_format = "pdf_document")
rstudioapi::viewer(gsub("\\.Rmd","\\.pdf",rstudioapi::getSourceEditorContext()$path))
```
