---
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
header-includes:
output: pdf_document
---

```{r setup0, echo=FALSE,purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Question 1**

```{r}
# Replace "NULL" with the proper code.
total_pres <- factorial(5) / factorial(5 - 2)
total_office <- factorial(5) / factorial(5 - 3)
total_dean <- factorial(5) / (factorial(2) * factorial(5 - 2))

```

**Question 2**

```{r}

simulate_roulette <- function(n) {
  # Define the wheel
  wheel <- c("00",0:36)
  
  # Define colour mapping
  red_numbers <- c(1, 3, 5, 7, 9, 12, 14, 16, 18, 19, 21, 23, 25, 27, 30, 32, 34, 36)
  black_numbers <- c(2, 4, 6, 8, 10, 11, 13, 15, 17, 20, 22, 24, 26, 28, 29, 31, 33, 35)
  
  # Simulate spins
  results <- sample(wheel, size = n, replace = TRUE)
  
  # Assign colours
  colours <- sapply(results, function(x) {
    if (x %in% red_numbers) {
      "Red"
    } else if (x %in% black_numbers) {
      "Black"
    } else {
      NA
    }
  })
  
  # Assign parity
  parity <- sapply(results, function(x) {
    if (x %in% red_numbers || x %in% black_numbers) {
      if (as.numeric(x) %% 2 ==0) {
        "Even"
      } else {
        "Odd"
      }
    } else {
      NA
    }
  })
  
  # Assign dozens
  dozen <- sapply(results, function(x) {
    if (x %in% red_numbers || x %in% black_numbers) {
      if (as.numeric(x) < 13) {
        "1st 12"
      } else if (as.numeric(x) < 27) {
        "2nd 12"
      } else {
        "3rd 12"
      }
    } else {
      NA
    }
  })
  
  # Assign column
  column <- sapply(results, function(x) {
    if (as.numeric(x) %in% seq(1,34,3)) {
      "1st Column"
    } else if (as.numeric(x) %in% seq(2,35,3)) {
      "2nd Column"
    } else if (as.numeric(x) %in% seq(3,36,3)) {
      "3rd Column"
    } else {
      NA
    }
  })
  
  # Assign high_low
  high_low <- sapply(results, function(x) {
    if (as.numeric(x) %in% 19:36) {
      "High"
    } else if (as.numeric(x) %in% 1:18) {
      "Low"
    } else {
      NA
    }
  })
  
  # Create data frame
  data.frame(Number = results, Colour = colours, Parity = parity, High_Low = high_low, Dozen = dozen, Column = column)
}
# Execute this code chunk before proceeding.
```

**Question 2 part (a)**

```{r,out.width='30%',fig.align='center'}
# Execute the simulate_roulette function and store the results appropriately below
roulette_plays <- simulate_roulette(500)
# Create a table:
table(roulette_plays$Column)
# Create a barplot of the table:
barplot(table(roulette_plays$Column))
```

**Question 2 part (b)**

```{r}
# Calculate the described probabilites and consider the results.
simulated <- NULL
theoretical <- NULL

```

**Question 3**

```{r}
# Code below creates a function simulating the game.
prize <- function(CHOICE = 1,CHANGE = "N",PLAYS = 1) {
  # Define an empty vector to store the results of the game:
  results <- c()
  # For the number of PLAYS, play the game
  for (i in 1:PLAYS) {
  # Randomly select a door for the car to be behind:
  car <- sample(1:3,1)
  if (CHOICE!=car & CHANGE == "Y") {
      results<- c(results,"WIN_CAR")
    } else if (CHOICE==car & CHANGE=="N") {
      results<- c(results,"WIN_CAR")
    } else {
      results<- c(results,"WIN_GOAT")
    }
  }
  return(results)
}
# Execute this code chunk before proceeding.
```

**Question 3 part (a)**

```{r}
# Run a single simulation of the game. View and understand the results.
prize(CHOICE = 2, CHANGE = "N", PLAYS = 1)
```

**Question 3 part (b)**

```{r}
# Run ten simulation of the game.
sims <- prize(CHOICE = 2, CHANGE = "N", PLAYS = 10)
# Create a table:
table(sims)
# Create a barplot of the table:
barplot(table(sims))
```

### Submission Instructions

1.  Save this file. (Quick key combo for that is "control" (or "command" on a Mac) and "s")
2.  Run the following code chunk to produce a pdf.
3.  Both of these files are likely in the "Downloads" folder (unless you moved them). Check the contents of each file and upload both the Rmd and pdf files to Gradescope.

```{r, echo=FALSE ,eval=FALSE,purl=FALSE}
rstudioapi::documentSave(rstudioapi::getSourceEditorContext()$id)
rmarkdown::render(rstudioapi::getSourceEditorContext()$path,output_format = "pdf_document")
rstudioapi::viewer(gsub("\\.Rmd","\\.pdf",rstudioapi::getSourceEditorContext()$path))
```
