---
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
header-includes:
output: pdf_document
---

```{r setup0, echo=FALSE,purl=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Question 1 part (a)**

```{r}
# Load the "iris" dataset to a variable called iris
data("iris")
# Print dataset
iris
# In the lab, `iris <- read.csv()` will likely be used to load a dataset in place of data()

```

**Question 1 part (b)**

```{r}
# This extracts the data from the `Petal.Length` variable in the `iris` dataset. 
# The result is treated as a vector in R. 
iris$Petal.Length

```

**Question 1 part (c)**

```{r}
vars <- names(iris)
n <- length(iris$Sepal.Length)
mean.SL <- mean(iris$Sepal.Length)
med.SL <- median(iris$Sepal.Length)
summary.PL <- summary(iris$Petal.Length)

```

**Question 1 part (d)**

```{r}
# set the plots to display in a 2 by 2 grid:
par(mfrow = c(2, 2)) # Don't modify this line
# Create a histogram of the `Petal.Length` variable in the `iris` dataset. Recall: `iris$Petal.Length` is the vector of data.
hist1 <- hist(iris$Petal.Length, main = "Histogram of Petal.Length", xlab = "Petal Length")
# Create a boxplot of the `Petal.Length` variable.
boxplot1 <- boxplot(iris$Petal.Length, main = "Boxplot of Petal.Length", ylab = "Petal Length")
# Create a bar plot of the `Species` variable.
barplot1 <- barplot(table(iris$Species), main = "Bar Chart of Species", ylab = "Frequency")
#Create a pie chart of the `Species` variable.
pie1 <- pie(table(iris$Species), main = "Pie Chart of Species")
# Once all four plots are ready, run the code chunk. You will be able to flip through the different plots by clicking on their specific icons below.

```

**Question 2 part (a)**

```{r,out.width='50%'}
sample1 <- runif(30, min = 0, max = 1)
samples <- replicate(1000, runif(30, min = 0, max = 1))
sample_means <- colMeans(samples)
hist2 <- hist(sample_means, 
              main = "Sampling Distribution of the Mean (Uniform[0,1])",
              xlab = "Sample Means",
              col = "skyblue", 
              border = "white")

```

### Submission Instructions

1.  Save this file. (Quick key combo for that is "control" (or "command" on a Mac) and "s")
2.  Run the following code chunk to produce a pdf.
3.  Both of these files are likely in the "Downloads" folder (unless you moved them). Check the contents of each file and upload both the Rmd and pdf files to Gradescope.

```{r, echo=FALSE ,eval=FALSE,purl=FALSE}
rstudioapi::documentSave(rstudioapi::getSourceEditorContext()$id)
rmarkdown::render(rstudioapi::getSourceEditorContext()$path,output_format = "pdf_document")
rstudioapi::viewer(gsub("\\.Rmd","\\.pdf",rstudioapi::getSourceEditorContext()$path))
```
